\documentclass[letterpaper, onecolumn, 10pt]{article}
\linespread{2.4}
%\documentclass[letterpaper, twocolumn, 10pt]{article}
%\usepackage{usenix}

\usepackage{multirow}
\usepackage{comment}
\usepackage{epsfig}
%\usepackage{kotex}
%\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{url}
\usepackage{subfig}
\usepackage{color}
\usepackage{xcolor}
\usepackage{cases}
\usepackage{graphicx}
%\usepackage{float}
%\usepackage{caption}

\begin{document}

\title{
\bf PCStream: Automatic Stream Allocation Using a Program Context-based Data Separator
}

%\numberofauthors{1}

\author{
{\rm Taejin Kim}\\
Seoul National University
\and 
{\rm Sungjin Lee}\\
DGIST
\and 
{\rm Sangwook Shane Hahn}\\
Seoul National University
\and 
{\rm Joo-Young Hwang(?)} \\
Samsung Electronics
\and 
{\rm Jihong Kim} \\
Seoul National University
}

\maketitle

\thispagestyle{empty}

\subsection*{Abstract}
Multi-streamed SSDs provide a special mechanism, called streams,
for a host system to prevent data with different lifetimes from being
mixed into the same block. 
Streams, when properly used, can
improve both the performance and lifetime of flash-based SSDs by
reducing the garbage collection overhead. 
Existing stream
management techniques, however, are limited to be used in
practice. 
All known techniques (except one) require manual data-to-stream 
mapping while the automatic technique does not work with
modern append-only workloads. 
In this paper, we propose
PCStream, a fully automatic stream management technique, which
works with append-only workloads as well as update workloads.
PCStream automates the data-to-stream mapping by exploiting an
observation that writes/updates from the same program context
tend to show the same lifetime. 
PCStream allocates a different
stream for each program context which are automatically identified
during the run time. 
Furthermore, when data mapped to the same
stream show large differences in their lifetimes, PCStream
dynamically refines the stream allocation during garbage collection.
Our experimental results show that PCStream can reduce the
garbage collection overhead as much as manual stream
management techniques while no code modification is necessary.
For a RocksDB benchmark, PCStream improved 66\% over 
exisiting automatic stream management technique.

\input{introduction}
\input{motivation}
\input{pcstream}
\input{experiment}
\input{discussion}
\input{conclusion}
\input{reference}
\end{document}
