\newpage
\bibliographystyle{abbrv}
\bibliography{sigproc}
\begin{thebibliography}{00}

\bibitem{T10}
SCSI Block Commnads-4 (SBC-4).
\url{http://www.t10.org/cgi-bin/ac.pl?t=f&f=sbc4r15.pdf}.

\bibitem{MultiStream}
J.-U. Kang, J. Hyun, H. Maeng, and S. Cho. The Multi-streamed Solid-State Drive.
In \textit{Proceedings of the 6th Workshop on Hot Topics in Storage and File Systems (HotStorage'14)}, 2014.

\bibitem{Level}
F. Yang, D. Dou, S. Chen, M. Hou, J.-U. Kang, and S. Cho.
Optimizing NoSQL DB on Flash: A Case Study of RocksDB.
In \textit{Proceedings of IEEE 15th International Conference on Scalable Computing
and Communications}. 2015.

\bibitem{FStream}
E. Rho, K. Joshi, S.-U. Shin, N.J. Shetty, J.-Y. Hwang, S. Cho. and D.DG. Lee. 
FStream: Managing Flash Streams in the File System.
In \textit{Proceedings of the 16th USENIX Conference on File and Storage Technologies (FAST'18)}, 2018.

\bibitem{AutoStream}
J. Yang, R. Pandurangan, C. Chio, and V. Balakrishnan.
AutoStream: Automatic Stream Management for Multi-streamed SSDs.
In \textit{Proceedings of 10th ACM International Systems and Storage Conference (SYSTOR'17)}, 2017.

\bibitem{PCHa}
K. Ha, and J. Kim.
A Program Context-Aware Data Separation Technique for Reducing Garbage Collection Overhead in NAND Flash Memory.
In \textit{Proceedings of International Workshop on Storage Network Architecture 
and Parallel I/Os (SNAPI'11)}, 2011.

\bibitem{RocksDB}
Facebook. https://github.com/facebook/rocksdb.

\bibitem{Cassandra}
Apache Cassandra. http://cassandra.apache.org.

\bibitem{PC}
C. Gniady, A.R. Butt, Y.C. Hu.
Program-Counter-Based Pattern Classification in Buffer Caching.
In \textit{Proceedings of 6th Symposium on Operating Systems Design and Implementation (OSDI'04)}, 2004.

\bibitem{PC2}
F. Zhou, J.R. von Behren, and E.A. Brewer.
Amp: Program Context Specific Buffer Caching.
In \textit{Proceedings of USENIX Annual Technical Conference (ATC'05)}, 2005.

\bibitem{HotCold}
J.-W Hsieh, T.-W. Kuo and L.-P. Chang.
Efficient Identification of Hot Data for Flash Memory Storage Systems.
In \textit{ACM Transactions on Storage, v.2, n.1, p.22-40.}, 2006.

\bibitem{LSM}
P. ONeil, E. Cheng, D. Gawlick, and E. ONeil.
The Log-Structured Merge-Tree (LSM-Tree).
In \textit{Acta Informatica, v.33, n.4, p.351-385}, 1996.

\bibitem{GCC}
R.M. Stallman, and GCC Developer Community.
Using the GNU Compiler Collection for GCC version 7.3.0.
https://gcc.gnu.org/onlinedocs/gcc-7.3.0/gcc.pdf. 2018.

\bibitem{TRIM}
Jonathan Corbet.
Block layer discard requests.
\url{https://lwn.net/Articles/293658/}.

\bibitem{AMF}
S. Lee, M. Liu, S. Jun, S. Xu, J. Kim, and Arvind.
Application-Managed Flash.
In \textit{Proceedings of 14th USENIX Conference on File and Storage
Technologies (FAST'16)}, 2016.

\end{thebibliography}
